How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-26 docs/PhysicsPaper/StokesErosion.tex
NM

As discussed in Section \ref{subsec:anis}, the anisotropy of the medium results from the combination of {\em shape} anisotropy, at the individual grain level, and {\em configurational anisotropy}, at the large-scale level. As detailed in Section \ref{subsec:anis}, the configurational anisotropy can be extracted by replacing any

>>>>

As discussed in Section \ref{subsec:anis}, the anisotropy of the medium results from the combination of {\em shape} anisotropy, at the individual grain level, and {\em configurational anisotropy}, at the large-scale level. As detailed in Section \ref{subsec:anis}, the configurational anisotropy can be extracted by replacing any collection of partially-eroded bodies with circles having the same areas and centers of mass and measuring the anisotropy of the resulting configuration. We perform this process at every time step in the simulation, and show in Fig.~\ref{fig3}(a) both permeabilities, $k_{11}^{(c)}$ and $k_{22}^{(c)}$, of the corresponding circle configurations. As seen in the figure, the permeabilities of the circle configurations always lie in between the true values $k_{11}$ and $k_{22}$ of the eroded geometries.
